A Study on Common Bug Fix Patterns in Rust

### 2022-10-13 main.tex
changed results a bit and added related works sec
citation added for intro
instructions in related work
edits to results
figs tikzisized

\usepackage{listings, listings-rust}
\lstset{escapeinside={<@}{@>}}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage{subfiles} % Best loaded last in the preamble
\input{defs}

@@

\section{Introduction}
\subfile{sections/introduction}

\section{Methodology}
\subfile{sections/methodology}

\section{Results}
\subfile{sections/results}

\section{Discussion}
\subfile{sections/discussion}

\section{Conclusion}
\subfile{sections/conclusion}

@@

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{RefJ}
% Format for Journal Reference
Author, Article title, Journal, Volume, page numbers (year)
% Format for books
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

>>>>

\usepackage{listings, listings-rust}
\lstset{escapeinside={<@}{@>}}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{graphs} 
\usetikzlibrary{matrix}
\usepackage{multirow}
% \usepackage[backend=bibtex, style=authoryear]{biblatex}
% \addbibresource{bibtex.bib}
\usepackage{subfiles} % Best loaded last in the preamble
\input{defs}

\tikzset{ 
    table/.style={
        matrix of nodes,
        row sep=-\pgflinewidth,
        column sep=-\pgflinewidth,
        nodes={
            rectangle,
            draw=black,
            align=center
        },
        minimum height=1.5em,
        text depth=0.5ex,
        text height=2ex,
        nodes in empty cells,
        column 1/.style={
            nodes={text width=5em,font=\bfseries, fill=gray!20}
        },
        column 2/.style={
            nodes={text width=4em,font=\bfseries}
        },
        column 3/.style={
            nodes={text width=5em,font=\bfseries}
        },
        column 4/.style={
            nodes={text width=5em,font=\bfseries}
        },  
        column 5/.style={
            nodes={text width=8em,font=\bfseries}
        },  
        column 6/.style={
            nodes={text width=5em,font=\bfseries}
        },  
        column 7/.style={
            nodes={text width=5em,font=\bfseries}
        },
        column 8/.style={
            nodes={text width=9em,font=\bfseries}
        },
        column 9/.style={
            nodes={text width=3em,font=\bfseries}
        }
    }
}

@@

\section{Introduction}
% rubber: depend sections/introduction.tex
\subfile{sections/introduction}

\section{Methodology}
% rubber: depend sections/methodology.tex
\subfile{sections/methodology}

\section{Results}
% rubber: depend sections/results.tex
\subfile{sections/results}

\section{Discussion}
% rubber: depend sections/discussion.tex
\subfile{sections/discussion}

\section{Related Work}
% rubber: depend sections/related.tex
\subfile{sections/related}

\section{Conclusion}
% rubber: depend sections/conclusion.tex
\subfile{sections/conclusion}

@@

% BibTeX users please use one of
\bibliographystyle{plain}      % basic style, author-year citations
% \bibliographystyle{spmpsci}      % mathematics and physical sciences
% \bibliographystyle{spphys}       % APS-like style for physics
\bibliography{refs}       % name your BibTeX data base
% \printbibliography[title={References}]  % name your BibTeX data base

% Non-BibTeX users please use
% \begin{thebibliography}{}
% %
% % and use \bibitem to create references. Consult the Instructions
% % for authors for reference list style.
% %
% \bibitem{RefJ}
% % Format for Journal Reference
% Author, Article title, Journal, Volume, page numbers (year)
% % Format for books
% \bibitem{RefB}
% Author, Book title, page numbers. Publisher, place (year)
% % etc
% \end{thebibliography}

### 2022-10-13 sections/methodology.tex
figs tikzisized

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{figs/extraction.drawio.pdf}
\caption{\label{fig:extraction}Extracting paths from an ASTDiff. the ASTDiff on left corresponds to the code change in the yellow box on the top right. A DFS search will identify three paths, shown in three different colors at right.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1\textwidth]{figs/essence.drawio.pdf}
    \caption{\label{fig:essence}Multiplying the number of occurrences of items observed in the tree by their respective weights, resulting in the essence of change (visualized with a circle pack figure at right). The left and right key value tables show the number of occurrences of each item and its respective weight, respectively.}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\begin{tikzpicture}[scale=0.7, transform shape,every node/.style={draw},minimum height=0.7cm]

    %% Left AST

    \draw (-1.5,1.5) node[shape=rectangle, minimum width=3cm,minimum height=5.4cm, rounded corners=1ex, xshift=1.5cm, yshift=-2.5cm](context){};

    \node[draw=none] at (0,1) {Context};

    \draw (0,0) node[](a1){ItemFn};
    \draw (0,-1) node[](a2){Local};
    \draw (0,-2) node[](a3){ExprCall};
    \draw (0,-3) node[](a4){args};

    \draw (-2,-5) node[shape=circle](null){null};

    \draw (0,-5) node[](b1){ExprReference};
    \draw (0,-6) node[](b2){Path};
    \draw (0,-7) node[](b3){Ident};
    \draw (0,-8) node[](b4){tail};

    \draw (3,-5) node[](c1){ExprMethodCall};
    \draw (3,-6) node[](c2){Path};
    \draw (3,-7) node[](c3){Ident};
    \draw (3,-8) node[](c4){head};

    \draw (5,-6.5) node[](d1){Ident};
    \draw (5,-7.5) node[](d2){clone};

    \draw[->]  (a1) -- (a2);
    \draw[->]  (a2) -- (a3);
    \draw[->]  (a3) -- (a4);

    \draw[->]  (context) -- (null);
    \draw[->]  (context) -- (b1);
    \draw[->]  (context) -- (c1);

    \draw[->]  (b1) -- (b2);
    \draw[->]  (b2) -- (b3);
    \draw[->]  (b3) -- (b4);

    \draw[->]  (c1) -- (c2);
    \draw[->]  (c2) -- (c3);
    \draw[->]  (c3) -- (c4);

    \draw[->]  (c1) -- (d1);

    \draw [->, red] plot [smooth, tension=1] coordinates { (2,1) (2,-3) (1.4,-5) (1.4,-8.5)};

    \draw [->, green] plot [smooth, tension=1] coordinates { (2.5,1) (3,-3) (5,-5) (4,-6.5) (3.7,-8.5)};

    \draw [->, purple] plot [smooth, tension=1] coordinates { (3,1) (3.5,-3) (5.5,-5) (5.5,-8.5)};

    %% Arrow

    \node[draw=none] at (5.1,-2.7) {Path Extraction};
    \draw [-stealth,double,line width=2,color=blue!40](4.1,-3.2) -- (6.3,-3.2);

    %% Code at top right

    \node (codeA) [fill=yellow!20, rounded corners=1ex] at (10, 0) {%
    \centering
    \begin{minipage}{10cm}
    \centering
    \begin{lstlisting}[language=Rust, style=colouredRust]
      fn sample() {
        // ...
        -- let receiver = foo(arg1, tail, head)
        ++ let receiver = foo(arg1, &tail, head.clone())
        // ...
      }
    \end{lstlisting}

    \end{minipage}%
    };

    %% Paths at right

    \draw (7.5,-2.5) node[fill=red!30](e1){ItemFn};
    \draw (7.5,-3.5) node[fill=red!30](e2){Local};
    \draw (7.5,-4.5) node[fill=red!30](e3){ExprCall};
    \draw (7.5,-5.5) node[fill=red!30](e4){ExprReference};
    \draw (7.5,-6.5) node[fill=red!30](e5){Path};
    \draw (7.5,-7.5) node[fill=red!30](e6){Ident};

    \node[draw=none, color=red] at (7.5,-8.3) {Path 1};

    \draw (10.5,-2.5) node[fill=green!20](f1){ItemFn};
    \draw (10.5,-3.5) node[fill=green!20](f2){Local};
    \draw (10.5,-4.5) node[fill=green!20](f3){ExprCall};
    \draw (10.5,-5.5) node[fill=green!20](f4){ExprMethodCall};
    \draw (10.5,-6.5) node[fill=green!20](f5){Path};
    \draw (10.5,-7.5) node[fill=green!20](f6){Ident};

    \node[draw=none, color=green] at (10.5,-8.3) {Path 2};
    \node[draw=none, color=green] at (10.5,-8.3) {Path 2};

    \draw (13.5,-2.5) node[fill=purple!20](g1){ItemFn};
    \draw (13.5,-3.5) node[fill=purple!20](g2){Local};
    \draw (13.5,-4.5) node[fill=purple!20](g3){ExprCall};
    \draw (13.5,-5.5) node[fill=purple!20](g4){ExprMethodCall};
    \draw (13.5,-6.5) node[fill=purple!20](g5){Path};
    \draw (13.5,-7.5) node[fill=purple!20](g6){clone};
    \node[draw=none, color=purple] at (13.5,-8.3) {Path 3};

    \draw[->]  (e1) -- (e2);
    \draw[->]  (e2) -- (e3);
    \draw[->]  (e3) -- (e4);
    \draw[->]  (e4) -- (e5);
    \draw[->]  (e5) -- (e6);

    \draw[->]  (f1) -- (f2);
    \draw[->]  (f2) -- (f3);
    \draw[->]  (f3) -- (f4);
    \draw[->]  (f4) -- (f5);
    \draw[->]  (f5) -- (f6);

    \draw[->]  (g1) -- (g2);
    \draw[->]  (g2) -- (g3);
    \draw[->]  (g3) -- (g4);
    \draw[->]  (g4) -- (g5);
    \draw[->]  (g5) -- (g6);

    \end{tikzpicture}

    \caption{\label{fig:extraction}Extracting paths from an ASTDiff. the ASTDiff on left corresponds to the code change in the yellow box on the top right. A DFS search will identify three paths, shown in three different colors at right.}

\end{figure}

@@

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale=0.7, transform shape, every node/.style={draw},minimum height=0.7cm]

        %% Left AST

        \draw (-1.5,1.5) node[shape=rectangle, minimum width=3cm,minimum height=5.4cm, rounded corners=1ex, xshift=1.5cm, yshift=-2.5cm](context){};

        \node[draw=none] at (0,1) {Context};

        \draw (0,0) node[](a1){ItemFn};
        \draw (0,-1) node[](a2){Local};
        \draw (0,-2) node[](a3){ExprCall};
        \draw (0,-3) node[](a4){args};

        \draw (-2,-5) node[shape=circle](null){null};

        \draw (0,-5) node[](b1){ExprReference};
        \draw (0,-6) node[](b2){Path};
        \draw (0,-7) node[](b3){Ident};
        \draw (0,-8) node[](b4){tail};

        \draw (3,-5) node[](c1){ExprMethodCall};
        \draw (3,-6) node[](c2){Path};
        \draw (3,-7) node[](c3){Ident};
        \draw (3,-8) node[](c4){head};

        \draw (5,-6.5) node[](d1){Ident};
        \draw (5,-7.5) node[](d2){clone};

        \draw[->]  (a1) -- (a2);
        \draw[->]  (a2) -- (a3);
        \draw[->]  (a3) -- (a4);

        \draw[->]  (context) -- (null);
        \draw[->]  (context) -- (b1);
        \draw[->]  (context) -- (c1);

        \draw[->]  (b1) -- (b2);
        \draw[->]  (b2) -- (b3);
        \draw[->]  (b3) -- (b4);

        \draw[->]  (c1) -- (c2);
        \draw[->]  (c2) -- (c3);
        \draw[->]  (c3) -- (c4);

        \draw[->]  (c1) -- (d1);

        %% Tables

        \matrix (table1) [table,text width=6em,nodes={scale=0.45,transform shape}] at (8.5,1)
        {
        Element & ItemFn  & Local & ExprCall & ExprReference & Path & Ident & ExprMethodCall & clone\\
        \# & 1 & 1 & 1 & 1 & 2 & 3 & 1 & 1 \\
        };

        \node[draw=none] at (8.2,0) {Multiply};
        \draw [-stealth,double,line width=1,color=blue!40](7,0.4) -- (7,-0.4);

        \matrix (table2) [table,text width=6em,nodes={scale=0.45,transform shape}] at (8.5,-1)
        {
        Element & ItemFn  & Local & ExprCall & ExprReference & Path & Ident & ExprMethodCall & clone\\
        weight & 0.0004 & 2.21e-05 & 8.68e-05 & 1 & 2.60e-05 & 2.76e-05 & 4.75e-05 & 1 \\
        };

        \node[draw=none] (circlepack) at (10.5,-6.2)
            {\includegraphics[width=0.7\textwidth]{figs/circlepack.png}};

        \node[draw=none] at (9,-2.3) {Visualizing Essence};
        \draw [-stealth,double,line width=1,color=blue!40](7,-1.6) -- (7.5,-3.4);

        \end{tikzpicture}

    \caption{\label{fig:essence}Multiplying the number of occurrences of items observed in the tree by their respective weights, resulting in the essence of change (visualized with a circle pack figure at right). The left and right key value tables show the number of occurrences of each item and its respective weight, respectively.}
\end{figure}
